---
title: "Introductory R Exercises"
output:
  html_document:
    number_sections: no
    toc: yes
---

## Exercise 1
#### 1.1. Use the `?` help operator to understand what the sample function does.

```{r}
# Write your answer here
```

#### 1.2. Create a vector `coeffs` of 3 coefficients for a quadratic equation, using the `sample` function. Draw a sample of size 3 from [-10,10] with replacement.

```{r}
# Write your answer here
```

#### 1.3. Determine the class of the vector `coeffs`.

```{r}
# Write your answer here
```

#### 1.4. Assign the 3 values from the vector `coeffs` to variables `a`, `b`, and `c`, respectively.

```{r}
# Write your answer here
```

#### 1.5. Evaluate the discriminant of the quadratic equation, which is calculated as (b^2 - 4ac).
```{r}
# Write your answer here
```

## Exercise 2
#### 2.1. What are the minimum and maximum concentrations at which the plants were tested in the `CO2` data set?
```{r}
# Write your answer here
```

#### 2.2. Let's add a new variable to the `CO2` dataframe named `conc_L`, which is the concentration in L/L (i.e., `conc_L` = `conc`/1000). Confirm that a new variable was added to the dataset by using the `names()` function.
```{r}
# Write your answer here
```

#### 2.3. Make a scatterplot of the uptake versus concentration from the `CO2` data set. Use a `col=CO2$Type` argument to differentiate the data by region. 

```{r}
# Write your answer here
```

## Exercise 3
#### 3.1. Create a subset `sub` of the `CO2` dataset that only contains `Quebec` data where `conc` are greater than or equal to 675.

```{r}
# Write your answer here
```

#### 3.2. The units of CO2 uptake are in umol/m^2 sec. Create a new column in the `sub` subset called `uptake_min`, which contains the CO2 uptake rate in minutes (i.e. the value multiplied by 60).

```{r}
# Write your answer here
```

#### 3.3. For all plants subject to a CO2 concentration greater than or equal to 500, what is the median uptake across each plant type, treatment, and CO2 concentration?

```{r}
# Write your answer here
```

#### 3.4. Determine how many (hint: `tally()`) plants of each `Type` experienced each condition (Treatment and concentration).
```{r}
# Write your answer here
```