---
title: "Exercises for Intermediate R"
output:
  html_notebook:
    number_sections: yes
    toc: yes
---

# Exercise 1 (P-001)

## How do you access an iris dataset?

```{r}
# Write R command(s) and run them to get the answer
iris

# ctrl + enter
```

```{r}
View(iris)
```

## How do can you get the meta information of this dataset? hint: use `?` command

```{r}
# Write R command(s) and run them to get the answer
?iris
```

### How many species are there and what are there?

__Answer__:
<!-- write your answer below -->
3

```{r}
length(unique(iris$Species))
```
```{r}
unique_species <- unique(iris$Species)
length(unique_species)
```
## How many rows are there in iris dataset?

```{r}
# Write R command(s) and run them to get the answer
nrow(iris)
```

## How many columns are there?

```{r}
# Write R command(s) and run them to get the answer
ncol(iris)
```

## What is the command that you can use to perform both?

```{r}
# Write R command(s) and run them to get the answer
dim(iris)
```

```{r}
?dim
```

## What is the data type for each column?

```{r}
# use ctrl + shift + enter to run all commands
class(iris)
class(iris$Sepal.Length)
str(iris) 
````

## what happens when you run a summary command on it?

```{r eval=FALSE}
summary(iris)
```


# Exercise 2 - Exploratory Data Analysis, Visualization (P-002)

## Import ggplot2

```{r}
library(ggplot2)
# Write R command(s) and run them to get the answer
```

## What do you see when you run this?

```{r eval=FALSE}
ggplot(data=iris, mapping=aes(x=Sepal.Length, y=Sepal.Width))
# Write R command(s) and run them to get the answer
```

```{r}
ggplot(data=iris, mapping=aes(x=Sepal.Length, y=Sepal.Width)) + 
  geom_point()
```
```{r}
ggplot(data=iris) + 
  geom_point(aes(x=Sepal.Length, y=Sepal.Width))
```

```{r}
p <- ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length, color=Species))
p +  geom_point()
p + geom_smooth()
```
```{r}
p + geom_smooth(aes(group=1))
```

## Plot the histogram of Sepal.Length

```{r}
# Write R command(s) and run them to get the answer
p2 <- ggplot(iris, aes(x=Sepal.Width))
p2 + geom_histogram(aes(fill=Species))
```

* What is the overall shape?
* How many peaks are there?


## Plot the histogram of Sepal.Length facetted by Species. Also fill the color by Species

```{r}
ggplot(iris, aes(x=Sepal.Length, fill=Species)) + 
  geom_histogram() +
  facet_wrap(~Species)
```

## Plot the boxplots of Sepal.Length by Species

```{r}
p <- ggplot(iris, aes(x=Species, y=Sepal.Length, fill=Species)) + 
  geom_boxplot() 
p + 
  labs(title="Sepal Length for each Iris Species", 
       subtitle="Virginica seems to be the longest in sepal length") + 
  theme_bw() + 
  theme(plot.title=element_text(size=30)) + 
  theme(axis.title.x=element_text(size=20)) + 
  theme(axis.text.x=element_text(size=15)) + 
  theme(axis.title.y=element_text(size=20)) +
  theme(legend.position="")
```



# Exercise 3 - P-003

# Load Caret

```{r}
library(caret)
# Write R command(s) and run them to get the answer
```

# Do 75% Train/Test split on iris dataset

```{r eval=FALSE}
set.seed(123)
idx_train <- caret::createDataPartition(
  y = iris$Species,
  p = .75,
  list = FALSE
)

data_train <- iris[idx_train, ]
data_test <- iris[-idx_train, ]

dim(data_train)
dim(data_test)
```

# Fit the random forest model with mtry=2

```{r}
model_rf <- caret::train(x=data_train[,1:4],
                         y=data_train$Species,
                         method='rf',
                         tuneGrid=data.frame(mtry=2),
                         trControl=trainControl(method="none")
                         )
model_rf
```


```{r}
data_pred <- predict(model_rf, newdata=data_test[, 1:4])
data_pred
```

```{r}
length(data_pred)
```

```{r}
caret::confusionMatrix(data_pred, data_test$Species)
```

# Do 5-fold cross-validation

```{r}
ctrl <- caret::trainControl(
  method = "cv",
  number = 5,
)

model_rf2 <- caret::train(
  x = data_train[,1:4],
  y = data_train$Species,
  trControl = ctrl,
  tuneGrid=data.frame(mtry=c(1,2,3,4)),
  method = "rf",
)
```


# Do the iris Species classification using 'k-nearest neighbor'


```{r}
# Write R command(s) and run them to get the answer
```

## What is the best K?
