---
title: "Exercises for Intermediate R"
output:
  html_notebook:
    number_sections: yes
    toc: yes
---

# Exercise 1 (P-001)

## How do you access an iris dataset?

```{r}
# Write R command(s) and run them to get the answer
```
## How do can you get the meta information of this dataset? hint: use `?` command

```{r}
# Write R command(s) and run them to get the answer
```

### How many species are there and what are there?

__Answer__:
<!-- write your answer below -->


## How many rows are there in iris dataset?

```{r}
# Write R command(s) and run them to get the answer
```

## How many columns are there?

```{r}
# Write R command(s) and run them to get the answer
```

## What is the command that you can use to perform both?

```{r}
# Write R command(s) and run them to get the answer
```

## What is the data type for each column?

```{r}
# Write R command(s) and run them to get the answer
```

## what happens when you run a summary command on it?

```{r eval=FALSE}
# Write R command(s) and run them to get the answer
```


# Exercise 2 - Exploratory Data Analysis, Visualization (P-002)

## Import ggplot2

```{r}
# Write R command(s) and run them to get the answer
```

## What do you see when you run this?

```{r eval=FALSE}
# Write R command(s) and run them to get the answer
```

## Plot the histogram of Sepal.Length

```{r}
# Write R command(s) and run them to get the answer
```

* What is the overall shape?
* How many peaks are there?


## Plot the histogram of Sepal.Length facetted by Species. Also fill the color by Species

```{r}
# Write R command(s) and run them to get the answer
```

## Plot the boxplots of Sepal.Length by Species

```{r}
# Write R command(s) and run them to get the answer
```



# Exercise 3 - P-003

# Load Caret

```{r}
# Write R command(s) and run them to get the answer
```

# Do 75% Train/Test split on iris dataset

```{r eval=FALSE}
# Write R command(s) and run them to get the answer
```

# Fit the random forest model with mtry=2

```{r}
# Write R command(s) and run them to get the answer
```

# Do 5-fold cross-validation

```{r}
# Write R command(s) and run them to get the answer
```


# Do the iris Species classification using 'k-nearest neighbor'


```{r}
# Write R command(s) and run them to get the answer
```

## What is the best K?
