---
title: "Exercises for Intermediate R"
output:
  html_notebook:
    number_sections: yes
    toc: yes
---

# Exercise 1 (P-001)

## How do you access an iris dataset?

```{r}
iris
# or
print(iris)
```
## How do can you get the meta information of this dataset? hint: use `?` command

```{r}
?iris
```

### How many species are there and what are there?

__Answer__:
<!-- write your answer below -->
three species: Iris setosa, versicolor, and virginica


## How many rows are there in iris dataset?

```{r}
nrow(iris)
```

## How many columns are there?

```{r}
ncol(iris)
```

## What is the command that you can use to perform both?

```{r}
dim(iris)
```

## What is the data type for each column?

```{r}
str(iris)
```

## what happens when you run a summary command on it?

```{r eval=FALSE}
summary(iris)
```


# Exercise 2 - Exploratory Data Analysis, Visualization (P-002)

## Import ggplot2

```{r}
library(ggplot2)
```

## What do you see when you run this?

```{r eval=FALSE}
ggplot(iris)
```

## Plot the histogram of Sepal.Length

```{r}
ggplot(iris, aes(x=Sepal.Length)) +
  geom_histogram()
```

* What is the overall shape?
* How many peaks are there?


## Plot the histogram of Sepal.Width

```{r}
ggplot(iris, aes(x=Sepal.Width)) +
  geom_histogram()
```

## Plot the boxplots of Sepal.Length by Species

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Length)) +
  geom_boxplot()
```





# Exercise 3


Run following

```{r eval=FALSE}
idx_train <- caret::createDataPartition(
  y = iris$Species,
  p = .75,
  list = FALSE
)
```


* Q: What does the above command return?


Check the dimension of each of train, test data set
