---
title: "Exercises for Intermediate R"
output:
  html_notebook:
    number_sections: yes
    toc: yes
---

# Exercise 1 (P-001)

## How do you access an iris dataset?

```{r}
iris
# or
print(iris)
```
## How do can you get the meta information of this dataset? hint: use `?` command

```{r}
?iris
```

### How many species are there and what are there?

__Answer__:
<!-- write your answer below -->
three species: Iris setosa, versicolor, and virginica
length(unique(iris$Species))

## How many rows are there in iris dataset?

```{r}
nrow(iris)
```

## How many columns are there?

```{r}
ncol(iris)
```

## What is the command that you can use to perform both?

```{r}
dim(iris)
```

## What is the data type for each column?

```{r}
str(iris)
```

## what happens when you run a summary command on it?

```{r eval=FALSE}
summary(iris)
```


# Exercise 2 - Exploratory Data Analysis, Visualization (P-002)

## Import ggplot2

```{r}
library(ggplot2)
```

## What do you see when you run this?

```{r eval=FALSE}
ggplot(iris)
```

## Plot the histogram of Sepal.Length

```{r}
ggplot(iris, aes(x=Sepal.Length)) +
  geom_histogram()
```

* What is the overall shape?
* How many peaks are there?


## Plot the histogram of Sepal.Length facetted by Species. Also fill the color by Species

```{r}
ggplot(iris, aes(x=Sepal.Length, fill=Species)) +
  geom_histogram() + 
  facet_wrap(~ Species)
```

## Plot the boxplots of Sepal.Length by Species

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Length)) +
  geom_boxplot()
```



# Exercise 3 - P-003

# Load Caret

```{r}
library(caret)
```

# Do 75% Train/Test split on iris dataset

```{r eval=FALSE}
idx_train <- caret::createDataPartition(
  y = iris$Species,
  p = .75,
  list = FALSE
)

data_all <- iris
data_train <- iris[idx_train, ]
data_test <- iris[-idx_train, ]
```

# Fit the random forest model with mtry=2

```{r}
model_rf <- caret::train(Species ~ . , 
                         data=data_train, 
                         method='rf', 
                         trControl=trainControl(method="none"),
                         tuneGrid=data.frame(mtry=1)
                         )
data_pred <- predict(model_rf, newdata=data_test[,1:4])
caret::confusionMatrix(data_pred, data_test$Species)
```

# Do 5-fold cross-validation

```{r}
ctrl_rf <- caret::trainControl(method = 'cv', number = 5)
model_rf <- caret::train(Species ~ . , 
                         data=data_train, 
                         trControl=ctrl_rf,
                         tuneGrid=data.frame(mtry=c(1,2,3,4)),
                         method='rf')
caret::confusionMatrix(predict(model_rf, newdata=data_test[,1:4]), data_test$Species)
ggplot(model_rf)
```


# Do the iris Species classification using 'k-nearest neighbor'


```{r}
ctrl_knn <- caret::trainControl(method = 'repeatedcv', number=5
                                , repeats = 10)
model_knn <- caret::train(Species ~ . ,
                      data=data_train,
                      trControl=ctrl_knn,
                      method='knn')
print(model_knn)
```
```{r}
ggplot(model_knn)
caret::confusionMatrix(predict(model_knn, newdata=data_test), data_test$Species)
```

## What is the best K?
